For_Clark

### 2020-07-16 Rcode/For_Clark.Rmd
update

New data mean in Parks 
L71 will need to be unhashed when working with our sample data - it selects only the months which have data in folder
L93 values need to change based on the length of your new filepath
```{r}

@@

# list_all<- list_all[c(1,4)] You will need to use this with our sample data folder

>>>>

New data mean in Parks 
L71 will need to be hashed out when working with full data - it selects only the months which have data in our sample folder
L93 values need to change based on the length of your new filepath
```{r}

@@

list_all<- list_all[c(1,4)] #You don't need this for final run with all data
